A performance comparison of Dask and Spark for data-intensive neuroimaging pipelines

### 2019-07-24 latex/paper.tex
Added new data and updated figures

%Similarities
Spark and Dask both offer in-memory computing, data locality, and lazy
evaluation; which is common for Big Data frameworks. Both their schedulers
operate dynamically, which is good when task runtimes are not known ahead of
time~\cite{Dask:15}. They also provide rich, high-level programming APIs,
and support a variety of infrastructure schedulers, such as Mesos (Spark
only), YARN, or HPC clusters (Dask only). Over these similarities, the
frameworks have differences.

@@

% Related work
Spark and Dask were both included in the evaluation reported
in~\cite{Mehta:17} that used a neuroimaging and an astronomy application
processing approximately 100~GB of data each. In this work, Dask was
reported to have a slight performance advantage over Spark. Overall, Dask's
end-to-end time (makespan) was measured to be up to 14\% faster than Spark,
due to ``more efficient pipelining'' %(Fig 10) 
and serialization time to
Python. % (Fig. 12-a)
Dask, however, was reported to have a larger startup
time than Spark. % (Fig. 12-c)
The analysis remains at a quite high level
though, leaving most of the observed performance difference unexplained. In
comparison, our study will provide a detailed analysis of performance
differences and similarities between Spark and Dask.

@@

\begin{table}[!t]
    \renewcommand{\arraystretch}{1.3}
    \caption{Parameters for the experiments}\label{tab:param}
    \centering
    \begin{tabular*}{\columnwidth}{llll}
    \hline
                        & Incrementation & Histogram             & BIDS Example          \\ \hline
    \# of worker        & 1, 2, 4, 8     & 1, 2, 4, 8            & 1, 2, 4, 8            \\
    \# of blocks        & 30, 125, 750   & 30, 125, 750          & 30, 125, 750          \\
    \# of iterations    & 1, 10, 100     & \multicolumn{1}{c}{-} & \multicolumn{1}{c}{-} \\
    Sleep delay {[}\SI{}{\second}{]} & 1, 4, 16, 64   & \multicolumn{1}{c}{-} & \multicolumn{1}{c}{-} \\ \hline
    \end{tabular*}
    \end{table}

>>>>

%Similarities
Spark and Dask both offer in-memory computing, data locality, and lazy evaluation;
which is common for Big Data frameworks. Both their schedulers operate dynamically,
which is good when task runtimes are not known ahead of time~\cite{Dask:15}. They
also provide rich, high-level programming APIs, and support a variety of
infrastructure schedulers, such as Mesos, YARN, or HPC clusters (Dask only). Over
these similarities, the frameworks have differences.

@@

% Related work
Spark and Dask were both included in the evaluation reported
in~\cite{Mehta:17} that used a neuroimaging and an astronomy application
processing approximately \SI{100}{\giga\byte} of data each. In this work, Dask was
reported to have a slight performance advantage over Spark. Overall, Dask's
end-to-end time (makespan) was measured to be up to 14\% faster than Spark,
due to ``more efficient pipelining'' %(Fig 10) 
and serialization time to
Python. % (Fig. 12-a)
Dask, however, was reported to have a larger startup
time than Spark. % (Fig. 12-c)
The analysis remains at a quite high level
though, leaving most of the observed performance difference unexplained. In
comparison, our study will provide a detailed analysis of performance
differences and similarities between Spark and Dask.

@@

\begin{table}[!t]
    \renewcommand{\arraystretch}{1.3}
    \caption{Parameters for the experiments}\label{tab:param}
    \centering
    \begin{tabular*}{\columnwidth}{llll}
    \hline
                        & Incrementation & Histogram             & BIDS Example          \\ \hline
    \# of worker        & 1, 2, 4, 8     & 1, 2, 4, 8            & 1, 2, 4, 8            \\
    \# of blocks        & 30, 125, 750   & 30, 125, 750          & \multicolumn{1}{c}{-} \\
    \# of iterations    & 1, 10, 100     & \multicolumn{1}{c}{-} & \multicolumn{1}{c}{-} \\
    Sleep delay {[}\SI{}{\second}{]} & 1, 4, 16, 64   & \multicolumn{1}{c}{-} & \multicolumn{1}{c}{-} \\ \hline
    \end{tabular*}
    \end{table}
